The greatest PoS tags, just the best really

### 2016-05-03 submission-petter.tex
Additions to data, more tables

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}

@@

\section{Previous/Related work}
\label{sec:prev}
Previous work related to our experiments with tag set modifications include
investigating the effects of PoS tag sets on tagging of Swedish
\cite{Meg:01,Meg:02,Meg:09} and English \cite{Mac:05}. The important difference
is that they investigate the effects of PoS tags on tagging, while we assess
its effects on a downstream application, namely syntactic parsing.

\section{Data}
\label{sec:data}
\subsection{The Norwegian Dependency Treebank}
We used the newly developed Norwegian Dependency Treebank (NDT)
\cite{Sol:Skj:Ovr:14}, which is the first publicly available treebank for
Norwegian (for our experiments). It was developed at the National Library of
Norway in collaboration with the University of Oslo, and contains manual
syntactic and morphological annotation. The treebank contains 311 000 tokens
of Bokmål and 303 000 tokens of Nynorsk, the morphological annotation of which
follows that of the Oslo-Bergen Tagger \cite{Hag:Joh:Nok:00,Sol:13}, which in
turn is largely based on the work of \newcite{Faa:Lie:Van:97}. The annotated
texts are mostly newspaper text, but also include government reports,
parliament transcripts and excerpts from blogs. The annotation process of the
treebank was supported by the Oslo-Bergen Tagger and then manually corrected by
annotators.

@@

\paragraph{PoS Tag Set}
The tag set consists of 12 morphosyntactic PoS tags, with 7 additional tags for
punctuation and symbols. The tag set is thus rather coarse-grained, with broad
categories such as \texttt{subst} (noun) and \texttt{verb} (verb).

\paragraph{Dependency Relations}

@@

%\begin{table}
    %\centering
    %%\smaller[0.5]
    %\begin{tabular}{@{}ll@{}}
        %\toprule
        %\textbf{Tag} & \textbf{Description} \\
        %\midrule
        %\texttt{adj|komp} & Comparative adjective \\
        %\texttt{adj|pos} & Positive adjective \\
        %\texttt{adj|sup} & Superlative adjective \\
        %\texttt{det|be} & Definite determiner \\
        %\texttt{det|ub} & Indefinite determiner \\
        %\texttt{pron|pers} & Personal pronoun \\
        %\texttt{pron|pers|akk} & Personal pronoun, accusative \\
        %\texttt{pron|pers|nom} & Personal pronoun, nominative \\
        %\texttt{pron|refl} & Reflexive pronoun \\
        %\texttt{pron|res} & Reciprocal pronoun \\
        %\texttt{pron|sp} & Interrogative pronoun \\
        %\texttt{subst|appell} & Common noun \\
        %\texttt{subst|appell|be} & Common noun, definite \\
        %\texttt{subst|appell|be|gen} & Common noun, definite, genitive \\
        %\texttt{subst|appell|ub} & Common noun, indefinite \\
        %\texttt{subst|appell|ub|gen} & Common noun, indefinite, genitive \\
        %\texttt{subst|prop} & Proper noun \\
        %\texttt{subst|prop|gen} & Proper noun, genitive \\
        %\texttt{verb|fin} & Finite verb \\
        %\texttt{verb|infin} & Nonfinite verb \\
        %\bottomrule
    %\end{tabular}
    %\caption{The optimized tag set.}
    %\label{optimizedtagset}
%\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{relsize}

@@

\section{Previous/Related work}
\label{sec:prev}
The lack of previous efforts on extrinsic evaluation of the effects of PoS
tag sets on downstream applications is considerable. We will, instead/however,
consider(/noe annet, considerable...consider)  papers that evaluate the effects
of PoS tag set granularity on PoS tagging.  This includes investigating the
effects of PoS tag sets on tagging of Swedish \cite{Meg:01,Meg:02,Meg:09} and
English \cite{Mac:05}. Increases in tagger accuracy does not readily translate
to improved parsing.

\section{Data}
\label{sec:data}
\subsection{The Norwegian Dependency Treebank}
We used the newly developed Norwegian Dependency Treebank (NDT)
\cite{Sol:Skj:Ovr:14}, which is the first publicly available treebank for
Norwegian. It was developed at the National Library of Norway in collaboration
with the University of Oslo, and contains manual syntactic and morphological
annotation. The treebank contains 311 000 tokens of Bokmål and 303 000 tokens
of Nynorsk.  The annotated texts are mostly newspaper text, but also include
government reports, parliament transcripts and excerpts from blogs. The
annotation process of the treebank was supported by the Oslo-Bergen Tagger and
then manually corrected by annotators.

@@

Linguistic motivation, insight, utility...

\paragraph{Morphological Annotation}
The morphological annotation follows that of the Oslo-Bergen Tagger
\cite{Hag:Joh:Nok:00,Sol:13}, which in turn is largely based on the work of
\newcite{Faa:Lie:Van:97}. The tag set of NDT is based on the tag set of the
Oslo-Bergen Tagger. The PoS tags are complemented by a set of available
morphological features, such as definiteness, number and tense. These features
are used in our tag set modifications, where the coarse PoS tag of relevant
tokens are concatenated with one or more of these features.  This allows us to
include more linguistic information in the tags. The tag set consists of 12
morphosyntactic PoS tags, with 7 additional tags for punctuation and symbols.
The tag set is thus rather coarse-grained, with broad categories such as
\texttt{subst} (noun) and \texttt{verb} (verb).

\paragraph{Syntactic Annotation} The syntactic annotation choices in NDT are
largely based on the Norwegian Reference Grammar \cite{Faa:Lie:Van:97}. The
annotation choices are outlined in Table \ref{ndtannotation}, taken from
\newcite{Sol:Skj:Ovr:14}, providing overview of the analyses of syntactic
constructions that often distinguish dependency treebanks, such as coordination
and the treatment of auxiliary and main verbs.

\begin{table} \centering
    %\smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Head} & \textbf{Dependent} \\
        \midrule
        Preposition & Prepositional complement \\
        Finite verb & Complementizer \\
        First conjunct & Subsequent conjuncts \\
        Finite auxiliary & Lexical/main verb \\
        Noun & Determiner \\
        \bottomrule
    \end{tabular}
    \caption{Annotation choices in NDT.}
    \label{ndtannotation}
\end{table}

@@

%\begin{table}
    %\centering
    %\smaller[0.5]
    %\begin{tabular}{@{}lllll@{}}
        %\toprule
        %\textbf{Tag Set} & \textbf{MFT} & \textbf{Accuracy} &
        %\textbf{LAS} & \textbf{UAS} \\
        %\midrule
        %Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        %Full & 85.15\% & 93.48\% & \textbf{87.15\%} & \textbf{90.39\%} \\
        %\bottomrule
    %\end{tabular}
    %\caption{Evaluation of tagging and parsing the development data with the two
        %initial tag sets.}
    %\label{inittagseteval}
%\end{table}

\begin{table*}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Category} & \textbf{Feature(s)} & \textbf{MFT} &
        \textbf{Accuracy} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \emph{Baseline} & --- & 94.14\% & 97.47\% & 87.01\% & 90.19\% \\
        Noun & Type, case \& definiteness & 89.61\% & 97.05\% & 88.81\% &
        91.73\% \\
        Verb & Finiteness & 93.72\% & 97.35\% & 87.30\% & 90.43\% \\
        Adjective & Degree & 94.13\% & 97.41\% & 87.29\% & 90.44\% \\
        Determiner & Definiteness & 94.13\% & 97.49\% & 87.30\% & 90.42\% \\
        Pronoun & Type \& case & 94.12\% & 97.51\% & 87.30\% & 90.41\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the most successful tag set
        modification for each category.}
    \label{respectiveresults}
\end{table*}

\begin{table}
    \centering
    \smaller[2]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj|komp} & Comparative adjective \\
        \texttt{adj|pos} & Positive adjective \\
        \texttt{adj|sup} & Superlative adjective \\
        \texttt{det|be} & Definite determiner \\
        \texttt{det|ub} & Indefinite determiner \\
        \texttt{pron|pers} & Personal pronoun \\
        \texttt{pron|pers|akk} & Personal pronoun, accusative \\
        \texttt{pron|pers|nom} & Personal pronoun, nominative \\
        \texttt{pron|refl} & Reflexive pronoun \\
        \texttt{pron|res} & Reciprocal pronoun \\
        \texttt{pron|sp} & Interrogative pronoun \\
        \texttt{subst|appell} & Common noun \\
        \texttt{subst|appell|be} & Common noun, definite \\
        \texttt{subst|appell|be|gen} & Common noun, definite, genitive \\
        \texttt{subst|appell|ub} & Common noun, indefinite \\
        \texttt{subst|appell|ub|gen} & Common noun, indefinite, genitive \\
        \texttt{subst|prop} & Proper noun \\
        \texttt{subst|prop|gen} & Proper noun, genitive \\
        \texttt{verb|fin} & Finite verb \\
        \texttt{verb|infin} & Nonfinite verb \\
        \bottomrule
    \end{tabular}
    \caption{The optimized tag set.}
    \label{optimizedtagset}
\end{table}

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Tag set} & \textbf{MFT} & \textbf{Accuracy} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Full & 85.12\% & 93.46\% & 87.13\% & 90.32\% \\
        Optimized & 89.20\% & 96.85\% & \textbf{88.87\%} & \textbf{91.78\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the optimized tag set, compared to
        the initial tag sets.}
    \label{finalresults}
\end{table}
